Concept Dev for COMP study

### 2019-11-11 concept_dev.tex
generic update

\section{Data and Methods} The following sections describe datasets and initial explorations.
\subsection{Year slices} Year slices were developed for all publications from 1996-2018. All publications of language `English', with at-least 2 references and a complete publication record in Scopus are selected. Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'. 
%\vspace{-7mm}
% latex table generated in R 3.5.1 by xtable 1.8-4 package
% Thu Aug 15 14:13:47 2019
\begin{table}[ht]
\caption{Summary of initial Scopus Analytical data set. The number of unique publications, unique references, total references . } 
\label{tab:summary_data}
\vspace{3 mm}
\centering
\scalebox{0.7}{
\begin{tabular}{|r rrr r|}
  \hline
 & Year & Unique Publications & Unique References & Total References \\ 
  \hline
1 & 1996 & 30783 & 185816 & 320533 \\ 
  2 & 1997 & 37284 & 230475 & 389779 \\ 
  3 & 1998 & 45198 & 254160 & 445703 \\ 
  4 & 1999 & 40776 & 241013 & 420839 \\ 
  5 & 2000 & 45310 & 266764 & 471079 \\ 
  6 & 2001 & 65168 & 357472 & 651196 \\ 
  7 & 2002 & 75583 & 410290 & 761714 \\ 
  8 & 2003 & 88701 & 458459 & 904755 \\ 
  9 & 2004 & 88984 & 506063 & 980388 \\ 
  10 & 2005 & 110741 & 609294 & 1247543 \\ 
  11 & 2006 & 140729 & 731622 & 1579690 \\ 
  12 & 2007 & 171357 & 845569 & 1879419 \\ 
  13 & 2008 & 205852 & 1019330 & 2281452 \\ 
  14 & 2009 & 239905 & 1239406 & 2841795 \\ 
  15 & 2010 & 255254 & 1391036 & 3214371 \\ 
  16 & 2011 & 255633 & 1534865 & 3464829 \\ 
  17 & 2012 & 264011 & 1700862 & 3845051 \\ 
  18 & 2013 & 261442 & 1866133 & 4199482 \\ 
  19 & 2014 & 272711 & 2004406 & 4581855 \\ 
  20 & 2015 & 309446 & 2220732 & 5202960 \\ 
  21 & 2016 & 316430 & 2422531 & 5630283 \\ 
  22 & 2017 & 308102 & 2622125 & 5918274 \\ 
  23 & 2018 & 340221 & 3012740 & 6960056 \\ 
   \hline
\end{tabular}}
\vspace{-1mm}
\end{table}

>>>>

\section{Data and Methods} The following sections describe datasets and initial explorations.
\subsection{Scopus Year slices} Year slices were developed for all publications from 1996-2018. All publications of language `English', with at-least 2 references and a complete publication record in Scopus are selected. Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'. 
\subsection{DBLP Data} Data from DBLP, for the years 1996-2018 were collected. A whole text matching approach (@dk) was used to match titles to Scopus identifiers. 
\subsection{Clustering}
%\vspace{-7mm}
% latex table generated in R 3.5.1 by xtable 1.8-4 package
% Thu Aug 15 14:13:47 2019
\begin{table}[ht]
\caption{Summary of initial Scopus Analytical data set. The number of unique publications, unique references, total references . } 
\label{tab:summary_data}
\vspace{3 mm}
\centering
\scalebox{0.7}{
\begin{tabular}{|r rrr r|}
  \hline
 & Year & Unique Publications & Unique References & Total References \\ 
  \hline
1 & 1996 & 30783 & 185816 & 320533 \\ 
  2 & 1997 & 37284 & 230475 & 389779 \\ 
  3 & 1998 & 45198 & 254160 & 445703 \\ 
  4 & 1999 & 40776 & 241013 & 420839 \\ 
  5 & 2000 & 45310 & 266764 & 471079 \\ 
  6 & 2001 & 65168 & 357472 & 651196 \\ 
  7 & 2002 & 75583 & 410290 & 761714 \\ 
  8 & 2003 & 88701 & 458459 & 904755 \\ 
  9 & 2004 & 88984 & 506063 & 980388 \\ 
  10 & 2005 & 110741 & 609294 & 1247543 \\ 
  11 & 2006 & 140729 & 731622 & 1579690 \\ 
  12 & 2007 & 171357 & 845569 & 1879419 \\ 
  13 & 2008 & 205852 & 1019330 & 2281452 \\ 
  14 & 2009 & 239905 & 1239406 & 2841795 \\ 
  15 & 2010 & 255254 & 1391036 & 3214371 \\ 
  16 & 2011 & 255633 & 1534865 & 3464829 \\ 
  17 & 2012 & 264011 & 1700862 & 3845051 \\ 
  18 & 2013 & 261442 & 1866133 & 4199482 \\ 
  19 & 2014 & 272711 & 2004406 & 4581855 \\ 
  20 & 2015 & 309446 & 2220732 & 5202960 \\ 
  21 & 2016 & 316430 & 2422531 & 5630283 \\ 
  22 & 2017 & 308102 & 2622125 & 5918274 \\ 
  23 & 2018 & 340221 & 3012740 & 6960056 \\ 
   \hline
\end{tabular}}
\vspace{-1mm}
\end{table}
